Background for transient faults in asynchronous circuits

### 2019-04-08 draft_together3.tex
edited til end.. need to motivate each lemma and possibly add new diagrams

\begin{lemma}[1]
If the A half of the fault tolerant circuit starts in a valid initial state, and where $\sigma$ is the trace of the fault tolerant circuit, then:
\begin{itemize}
\item  $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit, regardless of the wire values in the B half.
\item the logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
\item For all states $s$ in $\sigma$, $h^A(s)$ being excited corresponds to exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.  And $h^A(s)$ being unexcited corresponds to none of the four conditions are true.
\end{itemize}

@@

From state $s_k$, we look at all possible transitions; a transition may only occur on excited gates or c-elements.  If the transition occurs on the other half then no wire values changed in the A-half and the induction hypothesis remain true.  Thus we only need to consider the wires $w$ which are excited in the original circuit in state $h^A(s_k)$ and its corresponding wires in the A-half circuit.  For each excited wire $w$, the last induction hypothesis narrows the possible wires that can be excited in state $s_k$ and we examine the properties of the next state for each transition that can occur. %logic gate excited = c1^A excited
%possibly add graph to illustrate this
\begin{itemize}
\item The first case is for an excited wire $w$, the corresponding $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.  Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, thus wire $w$ satisfies the third induction hypothesis.  Since the transition occurred on an intermediate wire, the set of excited wires in state $h^A(s_{k+1})$ of the original circuit does not change and for both excited wires $v$ where $v\neq w$ and not excited wires the third induction hypothesis carries over from $s_k$ to $s_{k+1}$.  Thus the third induction hypothesis is true for all output wires.  Also since the output wires did not change, then $h^A(s_k)=h^A(s_{k+1})$ satisfying the first induction hypothesis.  The output wires not changing also allow the logic blocks to stay in a semi-modularity consistent state.   The induction hypotheses are true for any transition from this case.  %don't know if this needs to be explained more (and add that the non-excited wires are still non-excited?)
%since the inputs to the gate and the intermediate wires did not transition, then the gate is excited or $y^{A,B}\neq v^{A,B}$.  
%do I need to show that non-excited has nothing excited in duplicated
%$w$ is still excited in $h^A(s_{k+1})$ and in state $s_{k+1}$ only $c1^{A}\neq c2^{A}$ is true.   Therefore in this case the property is true for state $s_{k+1}$
\item The second case is when the signal propapagates down to $c2^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c1^A=c2^A$ and $c2^{A}\neq c3^{A}$ and thus wire $w$ satisfies the third induction hypothesis.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.   
\item The third case is similar to the second case and occurs when the signal propapagates down to $c3^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A$, $c2^{A}\neq c3^{A}$ and $c3^A=w^A$, then $c3^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c2^A=c3^A$ and $c3^{A}\neq w^{A}$ and thus wire $w$ satisfies the third induction hypothesis.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.

\item The fourth case is when the signal propapagates down to $w^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A=c3^A$ and $c3^A\neq w^A$, then $w^A$ transitions.  Since $w$ is excited in $h^A(s_k)$, then $T(h^A(s_k), h^A(s_{k+1}))$ which satisfies the first induction hypothesis.  Also since $h^A(s_{k+1})$ is a state in the original semi-modular circuit and the A-half logic blocks at state $s_k$ are semi-modularity consistent, inputs to all logic blocks in the A-half are also semi-modularity consistent. Then we look at the third induction hypothesis by splitting all of the wires into 4 subcases: the transitioning wire $w$; excited wires in state $h^A(s_k)$ other than $w$; newly excited wires in state $h^A(s_{k+1})$; and wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$.  (excited wires in $h^A(s_k)$ cannot be unexcited in $h^A(s_{k+1})$ by the semi-modularity property)  
\begin{itemize}
\item
$w$ is unexcited in state $h^A(s_{k+1})$ (we disregard the possibility that w can be immediately excited again), and in the A-half the changes are that $c3^{A}= w^{A}$.  Thus $w$ is unexcited and also the corresponding wires in the fault tolerant circuit are unexcited, wire $w$ satisfies the third induction hypothesis.  
\item
For any excited wire $v$ in state $h^A(s_k)$ and $v\neq w$, by semi-modularity of the original circuit $v$ is excited in state $h^A(s_{k+1})$ as well.  Thus, $c1^A$ of $v$ will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, wires of this type satisfy the third induction hypothesis.  
\item
For all newly excited wires $u$ in $h^A(s_{k+1})$, then in state $s_{k}$ $u$ is not excited in $h^A(s_k)$ and $c1^A=c2^A=c3^A=u^A=u$ and this is true in $s_{k+1}$ as well.  But since $u$ is excited then $c1^A$ in the A half must be excited.  Thus wires of this type satisfy the third induction hypothesis. 
\item
Finally for all other wires, ones that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, the logic gate is not excited and $c1^A=c2^A=c3^A=u^A$.  Thus wires of this type satisfy the third induction hypothesis.  
\end{itemize}
Then the induction hypotheses are true for any transition from this case. 
\end{itemize}
So the induction hypotheses holds for all possible $\sigma_{k+1}$ and the induction step is complete. \\
By induction on the length of the trace, the first property shows that $h^{A,B}(\sigma_n)$ is the prefix of a trace from the original circuit for all n.
%do I need to show the opposite?  At every step the previous transitions are possible??  Dunno if true for faults though.... also something about collapsed states can't tell the difference?  Can we just map it to a circuit where everything goes together? <- this needs proving?

@@

\begin{figure}
  \centering
    \includegraphics{flowl2c3}
  \caption{The wires in each row are in order of logic block, C1, C2, C3, W.  Each row represents half of the duplicated circuit, ie. top row are A half wires and bottom row are B half wires.  'Un' denotes that the logic block is unexcited and 'Exc' denotes the logic block is excited.  Blue arrows indicate a case change caused by transitions elsewhere in the circuit.  Black arrows indicate a wire transition.}
  \label{fig:l21}
\end{figure}
%fixed 
\begin{lemma}[2.1]
For any state in a trace of the fault tolerant circuit starting in a valid initial state, all wire blocks are in one of the cases in figure \ref{fig:l21}.
\end{lemma}
\begin{proof}
We show by induction that for the fault tolerant circuit, each wire block will be in one of the cases in the above figure.  The figure halves the number of cases, case 11 is the inversion of case 1 (with the 0's and 1's inverted) and from case 11 the state transition goes through the second half of the cases in figure \ref{fig:l21} but inverted.  Thus we only need to analyze up to case 10.  Because both halves satisfy the conditions of Lemma 1, those properties can be applied directly.\\

We look at the base case for every wire $w$ in the original circuit.  Because the duplicated circuit starts at the same valid initial state: $w=c1^A=c2^A=c3^A=w^A=c1^B=c2^B=c3^B=w^B$.  A wire $w$ can be either excited or unexcited in the original circuit. If the wire $w$ is unexcited, applying lemma 1,  A and B halves of $w$ in the duplicated circuit are in case 1 (or case 11, we will here on ignore the inverted 1's and 0's states, but each case technically represents two states).  If $w$ is excited then applying lemma 1 the logic blocks must be excited which is case 2.  Thus this property is true for the base case. \\

In the induction step, assume that the induction hypothesis is true for state $s_k$ and show it is true for $s_{k+1}$.  \\

We examine all possible $s_{k+1}$.  That is for all possible transitions from $s_k$, verify that each $s_{k+1}$ has output wire blocks that is in one of the cases in the above figure.  It is clear that the arrows point to next cases which can occur, thus we are verifying that there does not exist additional cases a transition can lead to, namely that the logic blocks does not behave inappropriately since the wires within the C-elements are self-contained.  Because the arrows do not always indicate wire transitions (some are transitions between excited or unexcited state of the logic blocks which are in response to transitions of other wires), we only need to verify that for the transitions that do occur (black arrows), it does not cause the other logic blocks to behave inappropriately.

@@

Case 2a/2b:  In case 2a, $c1^A$ is excited and can transition to case 3a.  Similarly case 2b can transition to case 3c.  From both cases it is possible that the unexcited logic block becomes excited and go to case 3b at the next state.  However the excited logic block cannot become unexcited (without the corresponding $c1$ transition) due to Semi-Modularity and lemma 1.

@@

Case 3a/3b/3c:  In case 3a (3c), it is possible for the logic block in B-half (A-half) to become excited, and change to 4a (4b).  The logic block in A-half (B-half) cannot be excited again with $c1^A=1$ ($c1^B=1$) because that violates lemma 1.  From 3b, when $c1^A$ or $c1^B$ transitions, the next state is 4a or 4b.  The excited logic blocks cannot become unexcited due to Semi-Modularity and lemma 1.

@@

The excited logic block in both cases can transition and end up in case 5.  The excited logic block cannot become unexcited due to Semi-Modularity and lemma 1.  The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (lemma 1).

@@

Cases 5/6a/6b/7/8a/8b:  In these cases for wire block $w$, the only wires able to transition are the excited C-element wires.  Thus case 5 transitions to case 6a or 6b, cases 6a or 6b transition to case 7, case 7 transitions to case 8a or 8b, and cases 8a or 8b transition to case 9.  The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (lemma 1).

@@

Cases 9/10a/10b:  In cases 1-8a/8b all the transition happen on intermediate wires so the state of the other wire blocks must remain the same.  In cases 9/10a/10b an output/input wire is changed so we must also consider the effects on the other wire blocks.  In case 9, when $w^a$ or $w^b$ is excited and transitions to 10a or 10b, an output wire is changed.  If any logic blocks are in case 9, its logic block cannot change excitations because it would violate lemma 1.  Thus far, we have shown why the logic blocks in cases 1-9 cannot change excitations other than those included in the figure.  We assume that the output wires cannot directly feed back into its logic block so that 10a or 10b cannot cause its logic block to be excited. For other logic blocks in case 10a or 10b, a transition in $w^A$ or $w^B$ cannot change the excitation in the other logic blocks.  This is shown by contradiction.  \\
Assume that there exists another logic block in case 10a and that $w^A$ transition causes an excitation in state $s_{k+1}$ (10a and 10b are symmetric so we only have to show for one of them).  All wire blocks are assumed to be in cases 1-10 in state $s_k$.  If there is an output wire mismatch such that for all wire $u\in W$ where $u^A\neq u^B$ then $c2^A=c2^B$ since it must be in cases 10a or 10b.  This is also true for those wires in state $s_{k+1}$ and the newly mismatched wire $w$.  Then from $s_{k+1}$ there exists a sequence of transitions of the mismatched wires so that they become equal in state $s_{k+1+m}$ (other than the one of interest).  In $s_{k+1+m}$ the excited logic block must still be excited due to semi-modularity.  But also the logic block in the other half must be excited since all of the input wires are equal.  This violates lemma 1 for that half and produces a contradiction.  Therefore a transition to 10a or 10b cannot excite the logic blocks in case 10a or 10b in other wire blocks.\\
From case 10a or 10b, there may be a transition to case 11 with a corresponding change in the output wires.  Again this cannot excite logic blocks of wires in case 10a or 10b by repeating the argument above in letting the circuit transition until there are no mismatched wires and causing a contradiction with lemma 1.

%still a slight problem here
\end{itemize}
This shows that all wire blocks in all possible $s_{k+1}$ remain in a case in the figure, and the induction step is complete.\\
By induction on the consecutive states of the trace, this shows that all wire blocks of a duplicated circuit are in a case in figure \ref{fig:l21} for all traces. \\
\end{proof}
%may be that I don't need how all the intermediate wires go... but just need the at most one of input excitation and outputs can be mismatched.  But this needs to include if outputs are mismatched then the C-element is the same.... which I think I need to show the signals propagating through??
\begin{lemma}[2.2]
For all traces $\sigma$ in the duplicated circuit (that start in the same valid initial state), deadlock does not occur.
\end{lemma}
\begin{proof}
To show that deadlock does not occur, we show that we can always find an excited wire at any state $s_k$ in a trace of the duplicated circuit.  $s_k$ can be split into two cases, one is that for every wire block $w$ all wires in the A half and B half are equal that is $w^A=w^B$, the second is that there exists at least one wire $v$ such that $v^A\neq v^B$.  In the first case, if every output wire pair are equal, then $h^A(s_n)=h^B(s_n)$ and there exists an excited wire $u$ in the original circuit.  By lemma 1 both halves of the duplicated circuit for $u$ is excited.  By the lemma 2.1, the circuit must be in case 2-6 for $u$.  In each of these cases at least one wire is excited.  \\
In the second case, for some wire $v$ such that $v^A\neq v^B$, then using lemma 2.1 wire block $v$ is in case 7a or 7b which has an excited wire, either $v^A$ or $v^B$.  Since there are next transitions for both cases, deadlock does not occur.
\end{proof}

Combining the results of the previous lemmas yield the following result:
\begin{theorem}[1]
For all traces $\sigma$ in the duplicated circuit starting from valid initial states, if $\sigma$ is a trace in the duplicated circuit and $\sigma_n$ is the sequence of the first n states of $\sigma$, then $h^{A,B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.  (h might make the trace shorter, so the prefix will not be of length n) %what was the point of the deadlock thing?
\end{theorem}

@@

\begin{definition}A transient fault on a wire $x$ can happen so that from the start of the transient fault $x= \lnot x^{init}$.  At some time later, the wire is able to transition again based on its inputs. %do I need to talk about when transient is not ~x?  ie hold same value?  That's the same as a longer delay

@@

Next we will show that adding a single transient fault to any wire will still allow one of the half circuits to progress as normal.  Since the 'good' half will always progress according to the original state graph if a transition is available, we just need to prove that it never deadlocks.  To do this we prove some properties that are true when we add a single transient fault.  We split the wires into two sets based on their properties when a single transient fault is added.  Lemma 3.1 shows that if a single fault is added to $c1$, $c2$ or $c3$ wires of the wire block for some wire $w$, the output wires still follow the original state graph.  Lemma 4 shows that if an fault is added to any of the other wires, then the $c1$, $c2$ or $c3$ wires follow a similar order to the non-fault case and thus the output wire pairs can never be different at deadlock.  Then we combine these lemmas to show that this implies that there is no deadlock.

@@

Without loss of generality we can show this is true if a transient fault occurs in the $A$ half.  We use NuSMV to verify that adding a transient fault to one of the $c2$ or $c3$ wires do not change the input-output characteristic of the local circuit.  Under normal operation, by lemma 2.1 the pair of inputs and outputs cycle through 00 00 00$\rightarrow$ 01 00 00 or 10 00 00 $\rightarrow$ 11 00 00 $\rightarrow$ 11 01 00 or 11 10 00 $\rightarrow$ 11 11 00 or 11 11 00 $\rightarrow$ 10 11 or 01 11 $\rightarrow$ 00 11 $\rightarrow$ 00 10 or 00 01 $\rightarrow$ 00 00.  Thus the property verified in NuSMV is that when a single transient fault can happen spontaneously on wires $c2$ or $c3$, the cycle mentioned previously is always true.    %We first deal with the $0\to 1 \to 0$ fault on $c2^A$.  
We go through an example of a transient on $c3^A$ to demonstrate why this happens.  By lemma 2.1 the normal circuit will be at some state in figure \ref{fig:l21}, so we analyze the transient occurring at each state in figure \ref{fig:l21}.

@@

\begin{lemma}[4]
For all traces $\sigma$ in the duplicated circuit, that allows adding a fault to any wire other than $c2$ or $c3$ at some time step $n$, the following property is true: the $c2$ and $c3$ wires of each wire $w\in W$ is always in a state of Figure \ref{fig:l4}.
\end{lemma}
\begin{proof}
Without loss of generality we prove this is true when a fault occurs in the A half.  Then we can assume Lemma 1 is true for the B half.  We show by induction that when the fault is not in $c2$ and $c3$, at any state $s_n$ from the trace $\sigma$, $c1$, $c2$ and $c3$ for all wires $w$ follow the state transitions in figure \ref{fig:l4}.  Again we only analyze for cases 1-5 as 6 onwards behave identically to cases 1-5 except with the 0's and 1's inverted.\\

The base case is for the valid initial state with no faults, projecting the states of figure \ref{fig:l21} from lemma 2 to just the $c1$, $c2$ and $c3$ wires shows this is true. \\

>>>>

\begin{lemma}[1]
If $\sigma$ is the trace of the fault tolerant circuit, then in the A half:
\begin{itemize}
\item  $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit, regardless of the wire values in the B half.
\item the logic blocks in the A half are semi-modularity consistent for all states in $\sigma$
\item For all states $s$ in $\sigma$, $h^A(s)$ being excited corresponds to exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$.  And $h^A(s)$ being unexcited corresponds to none of the four conditions are true.
\end{itemize}

@@

From state $s_k$, we look at all possible transitions; a transition may only occur on excited gates or c-elements.  If the transition occurs on the other half then no wire values changed in the A-half and the induction hypothesis remain true.  Thus we only need to consider the wires $w$ which are excited in the original circuit in state $h^A(s_k)$ and its corresponding wires in the A-half circuit.  For each excited wire $w$, the last induction hypothesis narrows the possible wires that can be excited in state $s_k$ and we examine the properties of the next state for each transition that can occur. %logic gate excited = c1^A excited
%possibly add graph to illustrate this
\begin{itemize}
\item The first case is for an excited wire $w$, the corresponding $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.  Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, thus wire $w$ satisfies the third induction hypothesis.  Since the transition occurred on an intermediate wire, the set of excited wires in state $h^A(s_{k+1})$ of the original circuit does not change and for both excited wires $v$ where $v\neq w$ and not excited wires the third induction hypothesis carries over from $s_k$ to $s_{k+1}$.  Thus the third induction hypothesis is true for all output wires.  Also since the output wires did not change, then $h^A(s_k)=h^A(s_{k+1})$ satisfying the first induction hypothesis.  The output wires not changing also allow the logic blocks to stay in a semi-modularity consistent state.   The induction hypotheses are true for any transition from this case.  %don't know if this needs to be explained more (and add that the non-excited wires are still non-excited?)
%since the inputs to the gate and the intermediate wires did not transition, then the gate is excited or $y^{A,B}\neq v^{A,B}$.  
%do I need to show that non-excited has nothing excited in duplicated
%$w$ is still excited in $h^A(s_{k+1})$ and in state $s_{k+1}$ only $c1^{A}\neq c2^{A}$ is true.   Therefore in this case the property is true for state $s_{k+1}$
\item The second case is when the signal propagates down to $c2^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c1^A=c2^A$ and $c2^{A}\neq c3^{A}$ and thus wire $w$ satisfies the third induction hypothesis.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.   
\item The third case is similar to the second case and occurs when the signal propagates down to $c3^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A$, $c2^{A}\neq c3^{A}$ and $c3^A=w^A$, then $c3^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c2^A=c3^A$ and $c3^{A}\neq w^{A}$ and thus wire $w$ satisfies the third induction hypothesis.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.

\item The fourth case is when the signal propagates down to $w^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A=c3^A$ and $c3^A\neq w^A$, then $w^A$ transitions.  Since $w$ is excited in $h^A(s_k)$, then $T(h^A(s_k), h^A(s_{k+1}))$ which satisfies the first induction hypothesis.  Also since $h^A(s_{k+1})$ is a state in the original semi-modular circuit and the A-half logic blocks at state $s_k$ are semi-modularity consistent, inputs to all logic blocks in the A-half are also semi-modularity consistent. Then we look at the third induction hypothesis by partitioning all of the wires into 4 subcases: the transitioning wire $w$; excited wires in state $h^A(s_k)$ other than $w$; newly excited wires in state $h^A(s_{k+1})$; and wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$.  (excited wires in $h^A(s_k)$ cannot be unexcited in $h^A(s_{k+1})$ by the semi-modularity property)  
\begin{itemize}
\item
$w$ is unexcited in state $h^A(s_{k+1})$ (we disregard the possibility that w can be immediately excited again), and in the A-half the changes are that $c3^{A}= w^{A}$.  Thus $w$ is unexcited and also the corresponding wires in the fault tolerant circuit are unexcited, wire $w$ satisfies the third induction hypothesis.  
\item
For any excited wire $v$ in state $h^A(s_k)$ and $v\neq w$, by semi-modularity of the original circuit $v$ is excited in state $h^A(s_{k+1})$ as well.  Thus, $c1^A$ of $v$ will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, wires of this type satisfy the third induction hypothesis.  
\item
For all newly excited wires $u$ in $h^A(s_{k+1})$, then in state $s_{k}$ $u$ is not excited in $h^A(s_k)$ and $c1^A=c2^A=c3^A=u^A=u$ and this is true in $s_{k+1}$ as well.  But since $u$ is excited then $c1^A$ in the A half must be excited.  Thus wires of this type satisfy the third induction hypothesis. 
\item
Finally for all other wires, ones that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, the logic gate is not excited and $c1^A=c2^A=c3^A=u^A$.  Thus wires of this type satisfy the third induction hypothesis.  
\end{itemize}
Then the induction hypotheses are true for any transition from this case. 
\end{itemize}
So the induction hypotheses holds for all possible $\sigma_{k+1}$ and the induction step is complete. \\
By induction on the length of the trace, the first property shows that $h^{A,B}(\sigma_n)$ is the prefix of a trace from the original circuit for all n.
%do I need to show the opposite?  At every step the previous transitions are possible??  Dunno if true for faults though.... also something about collapsed states can't tell the difference?  Can we just map it to a circuit where everything goes together? <- this needs proving?

@@

\begin{figure}
  \centering
    \includegraphics{flowl2c3}
  \caption{The wires in each row are in order of logic block, C1, C2, C3, W.  Each row represents half of the duplicated circuit, ie. top row are A half wires and bottom row are B half wires.  'Un' denotes that the logic block is unexcited and 'Exc' denotes the logic block is excited.  Blue arrows indicate a case change caused by transitions elsewhere in the circuit.  Black arrows indicate a wire transition.}
  \label{fig:l21}
\end{figure}
%fixed 
\begin{lemma}[2.1]
For any state in a trace of the fault tolerant circuit, the wire blocks are in one of the cases in figure \ref{fig:l21}.
\end{lemma}
\begin{proof}
We show by induction that for the fault tolerant circuit, each wire block is in one of the cases in the above figure.  The figure halves the number of cases, as case 11 is the inversion of case 1 (with the 0's and 1's inverted) and from case 11 the state transitions go through the same cases in figure \ref{fig:l21} from 1-11 but inverted.  Thus we only need to analyze possible transitions from each case up to case 10.  Also, Lemma 1 applies to both A half and B half.\\

We look at the base case for every wire $w$ in the original circuit.  Because the duplicated circuit starts at the same valid initial state: $w=c1^A=c2^A=c3^A=w^A=c1^B=c2^B=c3^B=w^B$.  A wire $w$ can be either excited or unexcited in the original circuit. If the wire $w$ is unexcited, applying lemma 1,  A and B halves of $w$ in the duplicated circuit are in case 1 (or case 11, we will here on ignore the inverted 1's and 0's states, but each case technically represents two states).  If $w$ is excited then Lemma 1 states that the logic blocks must be excited, which is case 2.  Thus this property is true for the base case. \\

In the induction step, assume that the induction hypothesis is true for state $s_k$ and we show that it is true for $s_{k+1}$.  \\

For all possible transitions from $s_k$, we verify that each $s_{k+1}$ has wire blocks that is in one of the cases in figure \ref{fig:l21}.  It is clear that the arrows represent transitions and logic block changes that can occur, thus we are verifying that there does not exist additional cases a transition can lead to, namely that the logic blocks does not behave inappropriately since the wires in the C-element chains behave as the arrows indicate.  Because the arrows do not always indicate wire transitions (some are transitions between excited or unexcited state of the logic blocks which are in response to transitions of other wires), we only need to verify that for the transitions that do occur (black arrows), it does not cause the other logic blocks to behave inappropriately.

@@

Case 2a/2b:  In case 2a, $c1^A$ is excited and can transition to case 3a.  Similarly case 2b can transition to case 3c.  From both cases it is possible that the unexcited logic block becomes excited and go to case 3b at the next state.  However the excited logic block cannot become unexcited (without the corresponding $c1$ transition) due to semi-modularity and Lemma 1.

@@

Case 3a/3b/3c:  In case 3a (3c), it is possible for the logic block in B-half (A-half) to become excited, and change to 4a (4b).  The logic block in A-half (B-half) cannot be excited again while $c1^A=1$ ($c1^B=1$) because that violates lemma 1.  From 3b, when $c1^A$ or $c1^B$ transitions, the next state is 4a or 4b.  The excited logic blocks cannot become unexcited due to semi-modularity and Lemma 1.

@@

A logic block is excited in both cases and can transition to case 5.  The excited logic block cannot become unexcited due to semi-modularity and Lemma 1.  The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (Lemma 1).

@@

Cases 5/6a/6b/7/8a/8b:  In these cases for wire block $w$, the only wires able to transition are the excited C-element wires.  Thus case 5 transitions to case 6a or 6b, cases 6a or 6b transition to case 7, case 7 transitions to case 8a or 8b, and cases 8a or 8b transition to case 9.  The already transitioned logic block (unexcited) cannot be excited again due to same reasoning as above (Lemma 1).

@@

Cases 9/10a/10b:  In cases 1-8a/8b all transitions happen on intermediate wires so the state of the other wire blocks must remain the same.  In cases 9/10a/10b an output/input wire is changed so we must also consider the effects on the other wire blocks.  In case 9, when $w^a$ or $w^b$ is excited and transitions to 10a or 10b, an output wire is changed.  If any logic blocks are in case 9, its logic block cannot change excitations because it would violate Lemma 1.  Thus far, we have shown why the logic blocks in cases 1-9 cannot change excitations other than when drawn in the figure.  The last step is to show that the logic blocks in case 10a or 10b also cannot change excitations.  \\  
We assume that the output wires cannot directly feed back into its logic block so that 10a or 10b cannot cause its own logic block to be excited.  For other logic blocks in case 10a or 10b, a transition in $w^A$ or $w^B$ cannot change the excitation in the other logic blocks.  This is shown by contradiction.  
Assume that there exists another logic block in case 10a and that the $w^A$ transition causes an excitation of wire $v$ in state $s_{k+1}$ (10a and 10b are symmetric so we only have to show for one of them).  In state $s_k$ an output wire mismatch is possible only if it is in cases 10a or 10b.  Thus for all wires $u$ where $u^A\neq u^B$, $c2^A=c2^B$ (which includes $v$).  $w^A$ transitioning does that change the values of those wires so the property is true in state $s_{k+1}$ as well.  It is also true of the newly mismatched wire $w$.  In other words all mismatched wires in $s_{k+1}$ have an output wire that is excited. Then from $s_{k+1}$ there exists a sequence of transitions of the mismatched wires so that they become equal in a later state (other than wire $v$).  In that later state, the excited logic block of $v$ must still be excited due to semi-modularity.  Since the input wires on both halves are equal, the logic block in the other half must be excited while its output wire is excited too.  This violates Lemma 1 and produces a contradiction.  Therefore a transition to 10a or 10b cannot excite the logic blocks in case 10a or 10b in other wire blocks.\\
From case 10a or 10b, there may be a transition to case 11 with a corresponding change in the output wires.  Again this cannot excite logic blocks of wires in case 10a or 10b by repeating the argument above in letting the circuit transition until there are no mismatched wires which contradicts Lemma 1.

%still a slight problem here
\end{itemize}
This shows that all wire blocks in all possible $s_{k+1}$ remain in a case in the figure, and the induction step is complete.\\
By induction on the consecutive states of the trace, the above argument shows that all wire blocks of a fault tolerant circuit are in a case in figure \ref{fig:l21} for all traces. \\
\end{proof}
%may be that I don't need how all the intermediate wires go... but just need the at most one of input excitation and outputs can be mismatched.  But this needs to include if outputs are mismatched then the C-element is the same.... which I think I need to show the signals propagating through??
It is now easy to show that deadlock does not occur since each wire block must be in one of the configurations of figure \ref{fig:l21}.
\begin{lemma}[2.2]
For all traces $\sigma$ in the fault tolerant circuit, deadlock does not occur.
\end{lemma}
\begin{proof}
To show that deadlock does not occur, we show that we can always find an excited wire at any state $s_k$ in a trace of the fault tolerant circuit.  The state $s_k$ can be split into two cases, one is that all output wire pairs in the A half and B half are equal, the second is that there exists at least one wire $v$ such that $v^A\neq v^B$.  In the first case, if every output wire pair are equal, then $h^A(s_n)=h^B(s_n)$ and there exists an excited wire $u$ in the original circuit.  By Lemma 1 both halves of the duplicated circuit for $u$ is excited.  By Lemma 2.1, the circuit must be in case 2-6 for $u$.  In each of these cases at least one wire is excited.  \\
In the second case, for some wire $v$ such that $v^A\neq v^B$, then using Lemma 2.1 wire block $v$ is in case 7a or 7b which has an excited wire, either $v^A$ or $v^B$.  Since there are next transitions for both cases, deadlock does not occur.
\end{proof}

Combining the results of the previous Lemmas yield the following result:
\begin{theorem}[1]
For all traces $\sigma$ in the fault tolerant circuit, where $\sigma_n$ is the sequence of the first $n$ states of $\sigma$, then $h^{A,B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.  (h might make the trace shorter, so the prefix will not be of length n) %what was the point of the deadlock thing?
\end{theorem}

@@

\begin{definition}A transient fault on a wire $w$ causes a transition $w= \lnot w^{prev}$.  After this event it is assumed that the wire can freely transition based on its inputs. %do I need to talk about when transient is not ~x?  ie hold same value?  That's the same as a longer delay

@@

Next we will show that if a single transient fault occurs on any wire, the half circuit that does not contain the fault will still transition normally.  Applying Lemma 1, we know that the 'good' half will transition according to the original state graph but it may deadlock, so we must prove that it does not deadlock.  To do this we prove some properties that are true when a single transient fault occurs on a wire.  We partition the wires into two sets based on their properties when a single transient fault is added.  Lemma 3.1 shows that if a single fault occurs on the $c2$ or $c3$ wires for some wire $w$, the output wires still follow the original state graph.  Lemma 4 shows that if a fault occurs to any of the other wires, then the $c2$ or $c3$ wires follow a similar order to the non-fault case and thus the output wire pairs can never be different at deadlock.  Then we combine these lemmas to show that this implies that there is no deadlock.

@@

Without loss of generality we can show this is true if a transient fault occurs in the $A$ half.  We use NuSMV to verify that if a transient fault occurs on one of the $c2$ or $c3$ wires of wire $w$, the input-output characteristic of the local C-element chain do not change.  Under normal operation, by Lemma 2.1 the pair of inputs ($c1^A$, $c1^B$) and outputs ($w^A$, $w^B$) cycle through 00 00 $\rightarrow$ 01 00 or 10 00 $\rightarrow$ 11 00 $\rightarrow$ 11 01 or 11 10 $\rightarrow$ 11 11 or 11 11 $\rightarrow$ 10 11 or 01 11 $\rightarrow$ 00 11 $\rightarrow$ 00 10 or 00 01 $\rightarrow$ 00 00.  Thus the property verified in NuSMV is that when a single transient fault occurs on wires $c2$ or $c3$, the cycle mentioned previously is always true.    %We first deal with the $0\to 1 \to 0$ fault on $c2^A$.  
We go through an example of a transient on $c3^A$ to demonstrate why this is true.  By Lemma 2.1 the normal circuit will be at some state in figure \ref{fig:l21}, so we analyze the transient occurring at each state in figure \ref{fig:l21}.

@@

\begin{lemma}[4]
For all traces $\sigma$ in the fault tolerant circuit, where a fault occurs on a wire other than $c2$ or $c3$, the following property is true: the $c2$ and $c3$ wires of each wire $w\in W$ are always in a state of Figure \ref{fig:l4}.
\end{lemma}
\begin{proof}
Without loss of generality we prove this is true when a fault occurs in the A half.  Then we can assume Lemma 1 is true for the B half.  We show by induction that when the fault is not in $c2$ and $c3$, at any state $s_n$ from the trace $\sigma$, $c1$, $c2$ and $c3$ for all wires $w$ follow the state transitions in figure \ref{fig:l4}.  Again we only analyze for cases 1-5 as 6 onwards behave identically to cases 1-5 except with the 0's and 1's inverted.\\

The base case is for the valid initial state with no faults, projecting the states of figure \ref{fig:l21} from Lemma 2 to just the $c1$, $c2$ and $c3$ wires shows this is true. \\
